---
title: "Air Pollution Effects on Enrollment"
author: "Vivan Malkani"
date: "January 15, 2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(velox)
library(raster)
library(readxl)
library(tidyverse)
library(sf)
library(ncdf4)
library(tiff)
```

2016 education outcome data source: National Institute of Educational Planning and Administration "District Report Cards". Annual enrollment for each district - includes breakdown of total enrollment by gender, caste religion, etc.
```{r}
education_2016 <- read_excel("DRC_Raw_Data 2016-17.xlsx", sheet = 2)
#eliminating extra rows
education_2016 = education_2016[21:nrow(education_2016),]
education_2016[1,1] = "Year"
colnames(education_2016) = education_2016[1,]
education_2016 = education_2016[2:nrow(education_2016),]
#selecting scheduled caste, tribe and muslim student enrollment.
education_2016_subset = education_2016 %>% 
  select(Year: DISTNAME,SCPTOT:MUUTOT_G)
```

India districts shapefile and PM2.5 data.
India map: Database of Global Administrative Areas
PM 2.5: Global Annual PM2.5 Grids from MODIS, MISR and SeaWiFS Aerosol Optical Depth (AOD) with GWR, v1 (1998-2016)
```{r}
india_districts = read_rds("gadm36_IND_2_sp.rds")
india_districts@data

#e <- extent(65, 95, 5, 35)
pm25_2016= raster("gwr_pm25_2016.tif") %>% crop(extent(india_districts))
#plot(pm25_2016)

pm_velox <- velox(pm25_2016)  #speedy extraction
pmVals <- pm_velox$extract(sp = india_districts, small = T)  #pm 2.5 readings for each district

plot(pm25_2016)

#mean pm 2.5 reading for each district
india_districts@data$pm <- lapply(pmVals, function(x){mean(x, na.rm = T)}) %>% 
  unlist() 
```
The Merge: joining by district name. Not using districts which have no education data.
```{r}

district_data = bind_cols("DISTNAME" = toupper(india_districts@data$NAME_2),
                          "STATNAME" = toupper(india_districts@data$NAME_1),
                          "PM2_5" = india_districts@data$pm)

d_names = district_data$STATNAME %>% unique() %>% sort()
e_names = education_2016_subset$STATNAME %>% unique() %>% sort()

#Name alignment for join
d_names[!d_names %in% e_names]
e_names[!e_names %in% d_names]

rm(d_names, e_names)

district_data = district_data %>%
  mutate(
    STATNAME = case_when(
      STATNAME == "ANDAMAN AND NICOBAR" ~ "A & N ISLANDS",
      STATNAME == "DAMAN AND DIU" ~ "DAMAN & DIU",
      STATNAME == "JAMMU AND KASHMIR" ~ "JAMMU & KASHMIR",
      STATNAME == "NCT OF DELHI" ~ "DELHI",
      STATNAME == "DADRA AND NAGAR HAVELI" ~ "DADRA & NAGAR HAVELI",
      TRUE ~ STATNAME
    )
  )
      

educ_PM = left_join(education_2016_subset, 
                    district_data,
                    by = c("DISTNAME", "STATNAME")) %>% 
  arrange(desc(PM2_5))

head(educ_PM, 5)
```

Other shapefile of India: backup merged dataset
```{r}
# india_districts_2016 = st_read("india-shapefile-3/polbnda_ind.shp") %>% arrange(nam, laa)
# 
# ggplot() + 
#   geom_sf(data = india_districts_2016, size = 0.3, color = "black") + 
#   ggtitle("India Districts") + 
#   coord_sf()
# 
# #e <- extent(65, 95, 5, 35)
# pm25_2016= raster("gwr_pm25_2016.tif") %>% crop(extent(india_districts_2016))
# #plot(pm25_2016)
# 
# 
# pm_velox <- velox(pm25_2016)  #make your raster a velox object
# pmVals <- pm_velox$extract(sp = india_districts_2016, small = T)  #as before, returns a list where each element is a vector of the pm values of cells falling into each country polygon
# 
# plot(pm25_2016)
# 
# india_districts_2016$pm <- lapply(pmVals, function(x){mean(x, na.rm = T)}) %>% 
#   unlist() 
```
```{r}
# district_data = bind_cols("STATNAME" = as.character(india_districts_2016$nam),
#                           "DISTNAME" = as.character(india_districts_2016$laa),
#                           "POPULATION" = india_districts_2016$pop,
#                           "PM2_5" = india_districts_2016$pm)
# 
# d_names = district_data$STATNAME %>% unique() %>% sort()
# e_names = education_2016_subset$STATNAME %>% unique() %>% sort()
# 
# d_names[!d_names %in% e_names]
# e_names[!e_names %in% d_names]
# 
# rm(d_names, e_names)
# 
# district_data = district_data %>%
#   mutate(
#     STATNAME = case_when(
#       STATNAME == "ANDAMAN AND NICOBAR" ~ "A & N ISLANDS",
#       STATNAME == "DAMAN AND DIU" ~ "DAMAN & DIU",
#       STATNAME == "JAMMU AND KASHMIR" ~ "JAMMU & KASHMIR",
#       STATNAME == "ORISSA" ~ "ODISHA",
#       STATNAME == "PONDICHERRY" ~ "PUDUCHERRY",
#       STATNAME == "TAMILNADU" ~ "TAMIL NADU",
#       STATNAME == "UTTARANCHAL" ~ "UTTARAKHAND",
#       STATNAME == "KARNATKA" ~ "KARNATAKA",
#       TRUE ~ STATNAME
#     )
#   )
#       
# 
# educ_PM = left_join(education_2016_subset, 
#                     district_data,
#                     by = c("DISTNAME", "STATNAME")) %>% 
#   arrange(STATNAME)
```
