---
title: "Air Pollution Effects on Enrollment"
author: "Vivan Malkani"
date: "January 15, 2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(velox)
library(raster)
library(readxl)
library(tidyverse)
library(dplyr)
library(sf)
library(ncdf4)
library(tiff)
library(RColorBrewer)
library(lfe)
library(rjson)
library(ggthemes)
library(stringr)
```

Education outcome data source: National Institute of Educational Planning and Administration "District Report Cards". Annual enrollment for each district - includes breakdown of total enrollment by gender, caste religion, etc.
```{r}
#Data Cleaning
education_2011 <- read_excel("DRC_Raw_Data 2011-12.xlsx", sheet = 3) %>% slice(17:n())
colnames(education_2011) <- education_2011[1,]

#Need to aggregate enrollment by class into "primary" and "upper primary", using schema of classes 1:5 as primary and 6:8 as upper primary. Also combining scheduled caste and tribe enrollment into one bin.
education_2011 <- education_2011 %>% 
  slice(2:n()) %>% 
  mutate(Year = "2011") %>%
  dplyr::select("Year", "State Name", "distname", "Enr Cy C1":"Stg Enrup Cy") %>%
  mutate(total_primary = as.integer(`Enr Cy C1`) + 
           as.integer(`Enr Cy C2`) + 
           as.integer(`Enr Cy C3`) + 
           as.integer(`Enr Cy C4`) + 
           as.integer(`Enr Cy C5`),
         total_upper = as.integer(`Enr Cy C6`) + 
           as.integer(`Enr Cy C7`) + 
           as.integer(`Enr Cy C8`),
         sc_st_primary = as.integer(`Sc Enrp Cy`) + as.integer(`St Enrp Cy`),
         sc_st_upper = as.integer(`Sc Enrup Cy`) + as.integer(`St Enrup Cy`),
         STATNAME = toupper(`State Name`),
         DISTNAME = toupper(distname)) %>%
  dplyr::select(Year, 
         STATNAME, 
         DISTNAME, 
         total_primary, 
         total_upper, 
         sc_st_primary, 
         sc_st_upper)

education_2012 <- read_excel("DRC_Raw_Data 2012-13.xlsx", sheet = 3) %>% slice(17:n())
colnames(education_2012) <- education_2012[1,]
education_2012 <- education_2012 %>% 
  slice(2:n()) %>% 
  mutate(Year = "2012") %>%
  dplyr::select(Year, "State Name", "distname", "Enr Cy C1": "Stg Enrup Cy") %>%
  mutate(total_primary = as.integer(`Enr Cy C1`) + 
           as.integer(`Enr Cy C2`) + 
           as.integer(`Enr Cy C3`) + 
           as.integer(`Enr Cy C4`) + 
           as.integer(`Enr Cy C5`),
         total_upper = as.integer(`Enr Cy C6`) + 
           as.integer(`Enr Cy C7`) + 
           as.integer(`Enr Cy C8`),
         sc_st_primary = as.integer(`Sc Enrp Cy`) + as.integer(`St Enrp Cy`),
         sc_st_upper = as.integer(`Sc Enrup Cy`) + as.integer(`St Enrup Cy`),
         STATNAME = toupper(`State Name`),
         DISTNAME = toupper(distname)) %>%
  dplyr::select(Year, 
         STATNAME, 
         DISTNAME, 
         total_primary, 
         total_upper, 
         sc_st_primary, 
         sc_st_upper)

education_2013 <- read_excel("DRC_Raw_Data 2013-14.xlsx", sheet = 3) %>% slice(17:n())
colnames(education_2013) <- education_2013[1,]
education_2013 <- education_2013 %>%
  slice(2:n()) %>%
  mutate(Year = "2013") %>%
  dplyr::select(Year, "State Name", "distname", "Enr Cy C1": "Stg Enrup Cy") %>%
  mutate(total_primary = as.integer(`Enr Cy C1`) + 
           as.integer(`Enr Cy C2`) + 
           as.integer(`Enr Cy C3`) + 
           as.integer(`Enr Cy C4`) + 
           as.integer(`Enr Cy C5`),
         total_upper = as.integer(`Enr Cy C6`) + 
           as.integer(`Enr Cy C7`) + 
           as.integer(`Enr Cy C8`),
         sc_st_primary = as.integer(`Sc Enrp Cy`) + as.integer(`St Enrp Cy`),
         sc_st_upper = as.integer(`Sc Enrup Cy`) + as.integer(`St Enrup Cy`),
         STATNAME = toupper(`State Name`),
         DISTNAME = toupper(distname)) %>%
  dplyr::select(Year, 
         STATNAME, 
         DISTNAME, 
         total_primary, 
         total_upper, 
         sc_st_primary, 
         sc_st_upper)

education_2014 <- read_excel("DRC_Raw_Data 2014-15.xlsx", sheet = 2)  %>% slice(19:n())
education_2014[1,1] = "Year"
colnames(education_2014) = education_2014[1,]
education_2014 <- education_2014 %>% slice(2:n()) %>% 
  dplyr::select("Year", "STATNAME", "DISTNAME", "C1_B":"C9_G", "SCPTOT":"STUTOT_G") %>%
  mutate(total_primary = as.integer(C1_B) + 
           as.integer(C2_B) + 
           as.integer(C3_B) + 
           as.integer(C4_B) + 
           as.integer(C5_B) +
           as.integer(C1_G) + 
           as.integer(C2_G) + 
           as.integer(C3_G) + 
           as.integer(C4_G) + 
           as.integer(C5_G),
         total_upper = as.integer(C6_B) + 
           as.integer(C7_B) + 
           as.integer(C8_B) +
           as.integer(C6_G) + 
           as.integer(C7_G) + 
           as.integer(C8_G),
         sc_st_primary = as.integer(SCPTOT) + as.integer(STPTOT),
         sc_st_upper = as.integer(SCUTOT) + as.integer(STUTOT),
         Year = "2014",
         STATNAME = toupper(STATNAME),
         DISTNAME = toupper(DISTNAME)) %>%
  dplyr::select(Year, 
         STATNAME,
         DISTNAME, 
         total_primary, 
         total_upper, 
         sc_st_primary, 
         sc_st_upper)

education_2015 <- read_excel("DRC_Raw_Data 2015-16_new.xlsx", sheet = 2) %>% slice(19:n())
education_2015[1,1] = "Year"
colnames(education_2015) = education_2015[1,]
education_2015 <- education_2015 %>% slice(2:n()) %>% 
  dplyr::select("Year", "STATNAME", "DISTNAME", "C1_B":"C9_G", "SCPTOT":"STUTOT_G") %>% 
  mutate(total_primary = as.integer(C1_B) + 
           as.integer(C2_B) + 
           as.integer(C3_B) + 
           as.integer(C4_B) + 
           as.integer(C5_B) +
           as.integer(C1_G) + 
           as.integer(C2_G) + 
           as.integer(C3_G) + 
           as.integer(C4_G) + 
           as.integer(C5_G),
         total_upper = as.integer(C6_B) + 
           as.integer(C7_B) + 
           as.integer(C8_B) +
           as.integer(C6_G) + 
           as.integer(C7_G) + 
           as.integer(C8_G),
         sc_st_primary = as.integer(SCPTOT) + as.integer(STPTOT),
         sc_st_upper = as.integer(SCUTOT) + as.integer(STUTOT),
         Year = "2015",
         STATNAME = toupper(STATNAME),
         DISTNAME = toupper(DISTNAME)) %>%
  dplyr::select(Year, 
         STATNAME,
         DISTNAME, 
         total_primary, 
         total_upper, 
         sc_st_primary, 
         sc_st_upper)

education_2016 <- read_excel("DRC_Raw_Data 2016-17.xlsx", sheet = 2) %>% slice(21:n())
education_2016[1,1] = "Year"
colnames(education_2016) = education_2016[1,]
education_2016 <- education_2016 %>% slice(2:n()) %>% 
  dplyr::select("Year", "STATNAME", "DISTNAME", "C1_B":"C9_G", "SCPTOT":"STUTOT_G") %>% 
  mutate(total_primary = as.integer(C1_B) + 
           as.integer(C2_B) + 
           as.integer(C3_B) + 
           as.integer(C4_B) + 
           as.integer(C5_B) +
           as.integer(C1_G) + 
           as.integer(C2_G) + 
           as.integer(C3_G) + 
           as.integer(C4_G) + 
           as.integer(C5_G),
         total_upper = as.integer(C6_B) + 
           as.integer(C7_B) + 
           as.integer(C8_B) +
           as.integer(C6_G) + 
           as.integer(C7_G) + 
           as.integer(C8_G),
         sc_st_primary = as.integer(SCPTOT) + as.integer(STPTOT),
         sc_st_upper = as.integer(SCUTOT) + as.integer(STUTOT),
         Year = "2016",
         STATNAME = toupper(STATNAME),
         DISTNAME = toupper(DISTNAME)) %>%
  dplyr::select(Year, 
         STATNAME,
         DISTNAME, 
         total_primary, 
         total_upper, 
         sc_st_primary, 
         sc_st_upper)

enrollment_data <- bind_rows(education_2011,
                             education_2012,
                             education_2013,
                             education_2014,
                             education_2015,
                             education_2016)

rm(education_2011, 
   education_2012,
   education_2013,
   education_2014,
   education_2015,
   education_2016)
```

India districts shapefile and PM2.5 data.
India map: Database of Global Administrative Areas
PM 2.5: Global Annual PM2.5 Grids from MODIS, MISR and SeaWiFS Aerosol Optical Depth (AOD) with GWR, v1 (1998-2016)
```{r}
india_districts = read_rds("gadm36_IND_2_sp.rds")
india_districts@data

#read in distinct global annual PM2.5 files and limit extent to India
pm25_2011= raster("gwr_pm25_2011.tif") %>% crop(extent(india_districts))
pm25_2012= raster("gwr_pm25_2012.tif") %>% crop(extent(india_districts))
pm25_2013= raster("gwr_pm25_2013.tif") %>% crop(extent(india_districts))
pm25_2014= raster("gwr_pm25_2014.tif") %>% crop(extent(india_districts))
pm25_2015= raster("gwr_pm25_2015.tif") %>% crop(extent(india_districts))
pm25_2016= raster("gwr_pm25_2016.tif") %>% crop(extent(india_districts))

pm_velox11 <- velox(pm25_2011) 
pm_velox12 <- velox(pm25_2012)
pm_velox13 <- velox(pm25_2013)
pm_velox14 <- velox(pm25_2014)
pm_velox15 <- velox(pm25_2015)
pm_velox16 <- velox(pm25_2016)

#extract PM2.5 reading for each district polygon for each year
pmVals_11 <- pm_velox11$extract(sp = india_districts, small = T)  #pm 2.5 readings for each district
pmVals_12 <- pm_velox12$extract(sp = india_districts, small = T)
pmVals_13 <- pm_velox13$extract(sp = india_districts, small = T)
pmVals_14 <- pm_velox14$extract(sp = india_districts, small = T)
pmVals_15 <- pm_velox15$extract(sp = india_districts, small = T)
pmVals_16 <- pm_velox16$extract(sp = india_districts, small = T)

#mean pm 2.5 reading for each district for each year
india_districts@data$pm11 <- lapply(pmVals_11, function(x){mean(x, na.rm = T)}) %>% 
  unlist() 
india_districts@data$pm12 <- lapply(pmVals_12, function(x){mean(x, na.rm = T)}) %>% 
  unlist() 
india_districts@data$pm13 <- lapply(pmVals_13, function(x){mean(x, na.rm = T)}) %>% 
  unlist() 
india_districts@data$pm14 <- lapply(pmVals_14, function(x){mean(x, na.rm = T)}) %>% 
  unlist() 
india_districts@data$pm15 <- lapply(pmVals_15, function(x){mean(x, na.rm = T)}) %>% 
  unlist() 
india_districts@data$pm16 <- lapply(pmVals_16, function(x){mean(x, na.rm = T)}) %>% 
  unlist() 

india_districts_sf <- st_as_sf(india_districts)

rm(pm_velox11, pm_velox12, pm_velox13, pm_velox14, pm_velox15, pm_velox16,
   pmVals_11, pmVals_12, pmVals_13, pmVals_14, pmVals_15, pmVals_16,
   pm25_2011, pm25_2012, pm25_2013, pm25_2014, pm25_2015, pm25_2016)
```

Downloading economic activity proxy: Night lights for economic activity proxy
```{r}
states = fromJSON(file = "http://api.nightlights.io/months/2008.1-2013.12/states")
state_names = vector()
for(i in 1:length(states)){
state_names[i] = states[[i]]$key
}
state_names = state_names %>% unique()

start_link = "http://api.nightlights.io/months/2008.1-2013.12/states/"
end_link = "/districts"

nightlights_districts = tibble("DISTNAME" = NA, "year" = NA, "month" = NA, "vis_median" = NA, "count" = NA)

for(i in 1:length(state_names)){
  state_data <- fromJSON(file = paste0(start_link,state_names[i],end_link))
  for(j in 1:length(state_data)){
    nightlights_districts = rbind(nightlights_districts, 
                                      c(state_data[[j]]$key,
                                        state_data[[j]]$year,
                                        state_data[[j]]$month,
                                        state_data[[j]]$vis_median,
                                        state_data[[j]]$count))
  }
}
nightlights_districts = slice(nightlights_districts, 2:n())

```

Converting to annual mean median visual intensity score for each district-year
```{r}
nightlights_annual = nightlights_districts %>% 
  group_by(DISTNAME, year) %>%
  summarise(vis_median = median(as.numeric(vis_median)),
            total_count = sum(as.numeric(count))) %>% 
  arrange(DISTNAME, year)
state_names <- state_names %>% sort()

nightlights_annual$STATNAME = NA
for(i in 1:length(state_names)){
  for(j in 1:nrow(nightlights_annual)){
    if(str_detect(nightlights_annual$DISTNAME[j], state_names[i])) {
      nightlights_annual$DISTNAME[j] = str_remove(nightlights_annual$DISTNAME[j], 
                                                  paste0(state_names[i], 
                                                         "-")) %>% 
        str_replace_all("-", " ") %>%
        toupper()
      nightlights_annual$STATNAME[j] = str_replace_all(state_names[i], "-", " ") %>% 
        toupper()
    }
  }
}



```


The Merge: joining by district name. Not using districts which have no education data.
```{r}

district_data = bind_cols("DISTNAME" = toupper(india_districts@data$NAME_2),
                          "STATNAME" = toupper(india_districts@data$NAME_1),
                          "2011" = india_districts@data$pm11,
                          "2012" = india_districts@data$pm12,
                          "2013" = india_districts@data$pm13,
                          "2014" = india_districts@data$pm14,
                          "2015" = india_districts@data$pm15,
                          "2016" = india_districts@data$pm16)

d_names = district_data$STATNAME %>% unique() %>% sort()
e_names = enrollment_data$STATNAME %>% unique() %>% sort()

#Name alignment for join
d_names[!d_names %in% e_names]
e_names[!e_names %in% d_names]

enrollment_data = enrollment_data %>%
  mutate(
    STATNAME = case_when(
      STATNAME == "A & N ISLANDS"|
        STATNAME == "ANDAMAN & NICOBAR ISLANDS" ~ "ANDAMAN AND NICOBAR",
      STATNAME == "CHHATISGARH" ~ "CHHATTISGARH",
      STATNAME == "D & N HAVELI"|
        STATNAME == "DADRA & NAGAR HAVELI" ~ "DADRA AND NAGAR HAVELI",
      STATNAME == "DAMAN & DIU" ~ "DAMAN AND DIU",
      STATNAME == "ORISSA" ~ "ODISHA",
      STATNAME == "JAMMU & KASHMIR" ~ "JAMMU AND KASHMIR",
      STATNAME == "DELHI" ~ "NCT OF DELHI",
      TRUE ~ STATNAME
    )
  )


rm(d_names, e_names)

district_data <- gather(district_data, "Year", "PM_25", -c(STATNAME, DISTNAME))

#for now, disregard all spelling inconsistencies between districts in each data set
educ_PM = inner_join(district_data,
                    enrollment_data, 
                    by = c("DISTNAME", "STATNAME", "Year"))

head(educ_PM, 5)

```
Population data (Census 2011) to convert enrollment to rate
```{r}
 census = read_excel("DDW_PCA0000_2011_Indiastatedist.xlsx", sheet = 1)
 
 households = census %>% 
   select(Level, Name, TRU, P_SC, P_ST) %>% 
   filter(Level == "DISTRICT" & TRU == "Total") %>%
   mutate(DISTNAME = toupper(Name)) %>%
   select(-Name, -Level, -TRU)

educ_PM_census = inner_join(educ_PM,
                     households, 
                     by = c("DISTNAME"))

educ_PM_census <- educ_PM_census %>% 
  mutate(SCST_total_rate = (sc_st_primary + sc_st_upper)/(P_SC + P_ST))
rm(educ_PM)
```

Bringing in night light controls
```{r}

d_names = educ_PM_census$STATNAME %>% unique() %>% sort()
e_names = nightlights_annual$STATNAME %>% unique() %>% sort()

#Name alignment for join
d_names[!d_names %in% e_names]
e_names[!e_names %in% d_names]

nightlights_annual = nightlights_annual %>%
  mutate(
    STATNAME = case_when(
      STATNAME == "TAMILNADU" ~ "TAMIL NADU",
      STATNAME == "ORISSA" ~ "ODISHA",
      STATNAME == "JAMMU & KASHMIR" ~ "JAMMU AND KASHMIR",
      STATNAME == "DELHI" ~ "NCT OF DELHI",
      TRUE ~ STATNAME
    )
  )

enroll_rate_PM_controls = inner_join(educ_PM_census, nightlights_annual, by = c("DISTNAME", "STATNAME", "Year" = "year"))
rm(educ_PM_census)
```



```{r}
ungrouped = filter(enroll_rate_PM_controls, DISTNAME != "MAHE")

grouped = filter(enroll_rate_PM_controls, DISTNAME != "MAHE") %>% 
  group_by(Year) %>% 
  summarise(med_PM = median(PM_25),
            lower_q_PM = quantile(PM_25, 0.25),
            upper_q_PM = quantile(PM_25, 0.75),
            b0 = coef(lm(SCST_total_rate ~ PM_25))[1],
            b1 = coef(lm(SCST_total_rate ~ PM_25))[2])

#Plotting PM 2.5 and Enrollment to show surprising results - likely confound
jpeg("Figure1_PM_enrollment.jpeg", quality = 100) 
ggplot() + geom_point(data = ungrouped,
                      aes(x = PM_25, y = SCST_total_rate),
                      size = 1,
                      alpha = 1/5) + 
  geom_smooth(data = ungrouped, aes(x = PM_25, y = SCST_total_rate), method = "lm", se = TRUE) + 
  xlab("PM 2.5 Concentration Levels (micrograms per cubic meter)") +
  ylab("Enrollment Rate from SC/ST Population") + 
  theme(axis.title = element_text(size=18, face = "bold"),
        axis.text = element_text(size = 12, face = "bold")) +
  geom_vline(data = grouped, aes(xintercept = med_PM)) + 
  geom_vline(data = grouped, aes(xintercept = lower_q_PM), linetype = "dashed") +
  geom_vline(data = grouped, aes(xintercept = upper_q_PM), linetype = "dashed") +
  theme_few() + 
  facet_wrap(~Year) + 
  theme(panel.spacing = unit(1.5, "lines"))
dev.off()


#Plotting with night light
ggplot(ungrouped) + 
  geom_histogram(aes(vis_median))

ggplot(ungrouped %>% filter(vis_median < 10)) + 
  geom_point(aes(vis_median, SCST_total_rate, color = PM_25)) + 
  geom_smooth(aes(vis_median, SCST_total_rate), method = "lm") +
  theme_clean()

  
```

India map enrollment plotting
```{r}
# 
# scst2011 <- educ_PM %>% filter(Year == 2011) %>% select(STATNAME, DISTNAME, SCST2011 = SCST_total)
# scst2012 <- educ_PM %>% filter(Year == 2012) %>% select(STATNAME, DISTNAME, SCST2012 = SCST_total)
# scst2013 <- educ_PM %>% filter(Year == 2013) %>% select(STATNAME, DISTNAME, SCST2013 = SCST_total)
# scst2014 <- educ_PM %>% filter(Year == 2014) %>% select(STATNAME, DISTNAME, SCST2014 = SCST_total)
# scst2015 <- educ_PM %>% filter(Year == 2015) %>% select(STATNAME, DISTNAME, SCST2015 = SCST_total)
# scst2016 <- educ_PM %>% filter(Year == 2016) %>% select(STATNAME, DISTNAME, SCST2016 = SCST_total)
# 
# india_districts_sf <- st_as_sf(india_districts)
# 
# india_districts_sf = india_districts_sf %>% mutate(STATNAME = toupper(NAME_1),
#                                                    DISTNAME = toupper(NAME_2))
# 
# india_districts_sf =  inner_join(india_districts_sf,
#                                  scst2011,
#                                  by = c("STATNAME", "DISTNAME"))
# india_districts_sf =  inner_join(india_districts_sf,
#                                  scst2012,
#                                  by = c("STATNAME", "DISTNAME"))
# india_districts_sf =  inner_join(india_districts_sf,
#                                  scst2013,
#                                  by = c("STATNAME", "DISTNAME"))
# india_districts_sf =  inner_join(india_districts_sf,
#                                  scst2014,
#                                  by = c("STATNAME", "DISTNAME"))
# india_districts_sf =  inner_join(india_districts_sf,
#                                  scst2015,
#                                  by = c("STATNAME", "DISTNAME"))
# india_districts_sf =  inner_join(india_districts_sf,
#                                  scst2016,
#                                  by = c("STATNAME", "DISTNAME"))
# 
# rm(scst2011, scst2012, scst2013, scst2014, scst2015, scst2016)

```

Figure 1 plotting
India PM2.5
```{r}

range = seq(0,125,by = 5)

png("india_districts_pm16.png")  
plot(india_districts_sf["pm16"], breaks = range, axes = FALSE)
title(main = "Average PM 2.5 micrograms per cubic meter in India (2016)",
      cex.main = 1,
      font.main= 4)
dev.off()

png("india_districts_pm15.png")  
plot(india_districts_sf["pm15"], breaks = range, axes = FALSE)
title(main = "Average PM 2.5 micrograms per cubic meter in India (2015)",
      cex.main = 1,
      font.main= 4)
dev.off()

png("india_districts_pm14.png")  
plot(india_districts_sf["pm14"], breaks = range, axes = FALSE)
title(main = "Average PM 2.5 micrograms per cubic meter in India (2014)",
      cex.main = 1,
      font.main= 4)
dev.off()

png("india_districts_pm13.png")  
plot(india_districts_sf["pm13"], breaks = range, axes = FALSE)
title(main = "Average PM 2.5 micrograms per cubic meter in India (2013)",
      cex.main = 1,
      font.main= 4)
dev.off()

png("india_districts_pm12.png")  
plot(india_districts_sf["pm12"], breaks = range, axes = FALSE)
title(main = "Average PM 2.5 micrograms per cubic meter in India (2012)",
      cex.main = 1,
      font.main= 4)
dev.off()

png("india_districts_pm11.png")  
plot(india_districts_sf["pm11"], breaks = range, axes = FALSE)
title(main = "Average PM 2.5 micrograms per cubic meter in India (2011)",
      cex.main = 1,
      font.main= 4)
dev.off()
```

Enrollment trends plotting, India map

```{r}
ggplot(india_districts_sf) + geom_histogram(aes(SCST2016), bins = 100)
ggplot(india_districts_sf) + geom_histogram(aes(SCST2015), bins = 100)
ggplot(india_districts_sf) + geom_histogram(aes(SCST2014), bins = 100)
ggplot(india_districts_sf) + geom_histogram(aes(SCST2013), bins = 100)
ggplot(india_districts_sf) + geom_histogram(aes(SCST2012), bins = 100)
ggplot(india_districts_sf) + geom_histogram(aes(SCST2011), bins = 100)

range = seq(-4,4,by = 0.4)

png("india_districts_scst16.png")  
plot(india_districts_sf["SCST2016"], breaks = range, axes = FALSE)
title(main = "Relative change in Enrollment of SC/ST Students (2016)",
      cex.main = 1,
      font.main= 4)
dev.off()

png("india_districts_scst15.png")  
plot(india_districts_sf["SCST2015"], breaks = range, axes = FALSE)
title(main = "Relative change in Enrollment of SC/ST Students (2015)",
      cex.main = 1,
      font.main= 4)
dev.off()

png("india_districts_scst14.png")  
plot(india_districts_sf["SCST2014"], breaks = range, axes = FALSE)
title(main = "Relative change in Enrollment of SC/ST Students (2014)",
      cex.main = 1,
      font.main= 4)
dev.off()

png("india_districts_scst13.png")  
plot(india_districts_sf["SCST2013"], breaks = range, axes = FALSE)
title(main = "Relative Change in Enrollment of SC/ST Students (2013)",
      cex.main = 1,
      font.main= 4)
dev.off()

png("india_districts_scst12.png")  
plot(india_districts_sf["SCST2012"], breaks = range, axes = FALSE)
title(main = "Relative change in Enrollment of SC/ST Students (2012)",
      cex.main = 1,
      font.main= 4)
dev.off()

png("india_districts_scst11.png")  
plot(india_districts_sf["SCST2011"], breaks = range, axes = FALSE)
title(main = "Relative change in Enrollment of SC/ST Students (2011)",
      cex.main = 1,
      font.main= 4)
dev.off()
```


```{r}
#bootstrap standard errors and plotting results
set.seed(1)

#Linear (log-log), district, SC/ST primary
dep = lm(log(SCST_total_rate) ~ Year + DISTNAME + vis_median, data=enroll_rate_PM_controls)
indep = lm(log(PM_25) ~ Year + DISTNAME + vis_median, data=enroll_rate_PM_controls)
plot(y = dep$residuals, x = indep$residuals)

#This is the data that you are visualizing

#Linear model, SC/ST total 
summary(felm(SCST_total_rate ~ PM_25 + vis_median | Year + DISTNAME,
             data=enroll_rate_PM_controls))

#Log- Linear model, SC/ST total 
summary(felm(log(SCST_total_rate) ~ PM_25 + vis_median | Year + DISTNAME,
             data=enroll_rate_PM_controls))

#Log - log model, SC/ST total 
summary(felm(log(SCST_total_rate) ~ log(PM_25) + vis_median | Year + DISTNAME,
             data=enroll_rate_PM_controls))

#Quadratic model, SC/ST total 
summary(felm(SCST_total_rate ~ poly(PM_25, 2, raw = T) + vis_median | Year + DISTNAME,
             data=enroll_rate_PM_controls))


#compare distributions of CV error




#see residual variation after regressing both independent and dependent on the fixed effects and plot actual residuals vs each other
#think about potential confounds that aren't handled by fixed effects (varying across state and time)
#log everything
#get confounds data - agriculture, income
#compare models - cross validate, f tests, out of sample prediction

```


Bootstrap
```{r}
b = 1000
n = nrow(educ_PM)

bootstrap<- function(){
  new_data = sample_n(educ_PM, n, replace = T)
  model = felm(sc_st_primary ~ poly(PM_25, 2, raw = T) | Year + STATNAME, data=new_data)
  coefficients = data.frame(model$coefficients)
  return(as.matrix(coefficients))
}

#creating sampling distribution of coefficient estimates
coef <- data.frame("b1"= 0, "b2" = 0)
for(i in 1:b){
  results = bootstrap()
  coef[i,1] = results[1]
  coef[i,2] = results[2]
}

#bootstrapped standard errors
sd(coef[,1])
sd(coef[,2])


```

Visualization
```{r}
pred_sc_st_p = educ_PM$PM_25*prelim_model$coefficients[1] + educ_PM$PM_25^2*prelim_model$coefficients[2]

plot(y = pred_sc_st_p, x= educ_PM$PM_25, type="p",las=1,ylab="SC/ST Primary Enrollment",xlab="PM 2.5 (micrograms per cubic meter)")

hist(educ_PM$PM_25, las=1,ylab="SC/ST Primary Enrollment",xlab="PM 2.5 (micrograms per cubic meter)")

educ_PM %>% 
  group_by(STATNAME) %>% 
  ggplot(aes(x = STATNAME, y = PM_25)) + 
  geom_boxplot() +
  facet_wrap(~STATNAME, scale="free")
```

*NOTES*
ADD CONTROLS LIKE ECONOMIC DEVELOPMENT: INCOME
ASSUMING 2016-17 = 2016
ASSUMING 1:5 = PRIMARY
6:8 UPPER PRIMARY
elementary education report card 2016-17 (andaman example), pg. 2
