---
title: "PM2.5 Enrollment Models"
author: "Vivan Malkani"
date: "February 16, 2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(velox)
library(raster)
library(readxl)
library(tidyverse)
library(dplyr)
library(sf)
library(ncdf4)
library(tiff)
library(RColorBrewer)
library(lfe)
library(rjson)
library(ggthemes)
library(stringr)
library(jtools)
library(ggstance)
library(huxtable)
library(gridExtra)
library(cowplot)
library(ggExtra)
library(boot)
```


```{r}
india_districts = st_read("india_districts.shp")
india_districts_sf = st_as_sf(india_districts)
enroll_rate_PM_controls = read_csv("enrollment_PM_NL_08-13.csv",  
                                   col_types = cols(Year = "f"))
NL_GDP = read_csv("NL_GDP_validation.csv",
                  col_types = cols(Year = "f") )
```

Visualizing distributions, deciding truncation and figure 1
```{r}
#Night Lights
ggplot(enroll_rate_PM_controls) + 
  geom_histogram(aes(vis_median))
#log to obtain normal distribution and +2 to get rid of negative numbers 
ggplot(enroll_rate_PM_controls) + 
  geom_histogram(aes(log(vis_median+2)))

#PM
ggplot(enroll_rate_PM_controls) + 
  geom_histogram(aes(PM_25))

#SCST Enrollment
ggplot(enroll_rate_PM_controls) + 
  geom_histogram(aes(SCST_total_rate))
#Truncate at 0.3
enroll_rate_PM_controls %>% filter(SCST_total_rate < 0.4) %>% nrow() / nrow(enroll_rate_PM_controls)
ggplot(enroll_rate_PM_controls %>% filter(SCST_total_rate < 0.4)) + 
  geom_histogram(aes(SCST_total_rate))

#Total Enrollment
ggplot(enroll_rate_PM_controls) + 
  geom_histogram(aes(total_rate))
#Truncate at 0.5
enroll_rate_PM_controls %>% filter(total_rate < 0.5) %>% nrow() / nrow(enroll_rate_PM_controls)
ggplot(enroll_rate_PM_controls %>% filter(total_rate < 0.5)) + 
  geom_histogram(aes(total_rate))




analysis_data = filter(enroll_rate_PM_controls, 
                   SCST_total_rate < 0.4, 
                   total_rate < 0.5) %>%
  mutate(log_vis = log(vis_median+2)) %>%
  mutate(Year = as.factor(Year))

grouped = filter(enroll_rate_PM_controls, 
                 SCST_total_rate < 0.4, 
                   total_rate < 0.5) %>% 
  group_by(Year) %>% 
  summarise(med_PM = median(PM_25),
            lower_q_PM = quantile(PM_25, 0.25),
            upper_q_PM = quantile(PM_25, 0.75),
            med_rate = median(total_rate),
            lower_rate = quantile(total_rate, 0.25),
            upper_rate = quantile(total_rate, 0.75))

#Total per 100,000
ggplot(analysis_data) + 
  geom_histogram(aes(total_per))
#SCST per 100,000
ggplot(analysis_data) + 
  geom_histogram(aes(SCST_per))

ggplot(filter(analysis_data, log(PM_25)>2.4)) + geom_histogram(aes(log(PM_25)))

dep_total = lm(total_rate ~ log_vis + Year + DISTNAME,
             data = analysis_data)
indep = lm(PM_25 ~ log_vis + Year + DISTNAME,
             data = analysis_data)

ggplot() + geom_point(aes(indep$residuals, dep_total$residuals)) +
  geom_smooth(aes(indep$residuals, dep_total$residuals),
              method = "lm", color = "red")

high_df = analysis_data %>% 
         mutate(high = ifelse(total_rate>.1667,1,0)) %>% 
         group_by(high)

ggplot(data = high_df, aes(PM_25, fill = high)) + 
  geom_histogram(alpha = 0.5, position = "identity") +  
  geom_vline(xintercept = 15, linetype = "dashed", size = 2) + 
  geom_vline(xintercept = mean(analysis_data$PM_25), size = 2) +
  xlab("Median Annual PM2.5 Level (μg/m^3)") +
  ylab("Number of Districts")+
  theme_clean() +
  facet_wrap(~high)
#Secondary standards provide public welfare protection, including protection against decreased visibility and damage to animals, crops, vegetation, and buildings.

analysis_data %>% group_by(Year) %>% summarize(median_PM = median(PM_25))
```

Figure 1: Visualize PM 2.5 variation
```{r}
visual_pm = india_districts_sf %>% 
  rowwise() %>% 
  mutate(median_pm = median(c(pm08, pm09, pm10, pm11, pm12, pm13))) %>%
  ungroup() %>%
  select(median_pm, geometry)

india_districts_sf$median_pm = visual_pm$median_pm

p1 = ggplot() +
  geom_sf(data = india_districts_sf, aes(fill = median_pm), color = NA) + 
  theme_void() +
  theme(axis.text = element_blank(),
        axis.ticks = element_blank(),
        legend.title = element_text(face = "bold", 
                                    size = 10),
        legend.position = "bottom",
        legend.box = "horizontal") +
  scale_fill_gradient(name= "Median PM 2.5 (μg/m^3)",
                        limits = c(0,100), 
                        breaks=c(0,20,40,60,80,100), 
                        na.value = "grey50")
# p2 = ggplot(analysis_data) + 
#   geom_point(aes(PM_25, SCST_total_rate), alpha = 0.1) + 
#   geom_smooth(aes(PM_25, SCST_total_rate), method = "lm") +
#   theme_classic() +
#   theme(panel.grid.major = element_blank(), 
#         panel.grid.minor = element_blank(),
#         axis.title = element_text(size = 12)) +
#   xlab("Median Annual PM2.5 Level (μg/m^3)") +
#   ylab("SC/ST enrollment rate")

p3 = ggplot(analysis_data) + 
  geom_point(aes(PM_25, total_rate), alpha = 0.1) + 
  geom_smooth(aes(PM_25, total_rate), method = "lm") +
  theme_classic() +
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        axis.title = element_text(size = 10)) +
  xlab("Median Annual PM2.5 Level (μg/m^3)") +
  ylab("Total enrollment rate")

pdf("figure1_v3.pdf", width = 7, height = 5)
plot_grid(p3, p1, ncol = 2,labels = c("a","b"), rel_widths = c(1,1.75), label_size = 12)
dev.off()
```


Creating different models
```{r}
linear_model_total = felm(total_rate ~ PM_25 + log_vis + total_count | Year + DISTNAME,
             data = analysis_data)
linear_model_SCST = felm(SCST_total_rate ~ PM_25 + log_vis + total_count | Year + DISTNAME,
             data = analysis_data)

simple_linear_total = felm(total_rate ~ PM_25|Year + DISTNAME, data = analysis_data)
simple_linear_SCST = felm(SCST_total_rate ~ PM_25|Year + DISTNAME, data = analysis_data)

no_log_total_rate = felm(total_rate ~ PM_25 + vis_median + total_count |Year + DISTNAME, data = analysis_data)
no_log_SCST_rate = felm(SCST_total_rate ~ PM_25 + vis_median + total_count |Year + DISTNAME, data = analysis_data)


gdp_pm_educ = inner_join(analysis_data, NL_GDP, by = c("DISTNAME", "STATNAME", "Year", 
                                                       "total_count", "vis_median"))
gdp_total_rate = felm(total_rate ~ PM_25 + log(GDP) + total_count |Year + DISTNAME, data = gdp_pm_educ)
gdp_SCST_rate = felm(SCST_total_rate ~ PM_25 + log(GDP) + total_count |Year + DISTNAME, data = gdp_pm_educ)

limited_NL = felm(total_rate ~ PM_25 + log_vis + total_count | Year + DISTNAME,
             data = gdp_pm_educ)
both_NL_GDP = felm(total_rate ~ PM_25 + log_vis + total_count + log(GDP) | Year + DISTNAME,
             data = gdp_pm_educ)
```

SC/ST RATE OF ENROLLMENT details
```{r}

#Linear (log-log), district, SC/ST primary
dep = lm(SCST_total_rate ~ Year + DISTNAME + log_vis, data=analysis_data)
indep = lm(PM_25 ~ Year + DISTNAME + log_vis, data = analysis_data)
plot(y = dep$residuals, x = indep$residuals)
#Validity limited to +- 10% enrollment effects and +- 20 PM 2.5

#Linear model, SC/ST total 

summary(linear_model_SCST)
#Check if error is normally distributed
ggplot() + geom_histogram(aes(linear_model_SCST$residuals))
#Check if predictions have patterns / heteroskedasticity
ggplot() + geom_point(aes(linear_model_SCST$fitted.values, analysis_data$SCST_total_rate))
ggplot() + geom_point(aes(analysis_data$PM_25, linear_model_SCST$residuals)) +
  geom_smooth(aes(analysis_data$PM_25, linear_model_SCST$residuals), 
              method = "lm")



#Diagnostics: checking with only NL and only PM 2.5
summary(felm(SCST_total_rate ~ log_vis | Year + DISTNAME,
             data = analysis_data))

summary(felm(SCST_total_rate ~ PM_25 | Year + DISTNAME,
             data = analysis_data))

summary(felm(PM_25 ~ log_vis | Year + DISTNAME,
             data = analysis_data))

```

TOTAL RATE OF ENROLLMENT details
```{r}

summary(felm(total_rate ~ log_vis | Year + DISTNAME,
             data = analysis_data))

summary(felm(total_rate ~ PM_25 | Year + DISTNAME,
             data = analysis_data))

summary(felm(PM_25 ~ log_vis | Year + DISTNAME,
             data = analysis_data))

#Linear model, total 

summary(linear_model_total)
#Check if error is normally distributed
ggplot() + geom_histogram(aes(linear_model_total$residuals))
#Check if predictions have patterns / heteroskedasticity
ggplot() + geom_point(aes(linear_model_total$fitted.values, analysis_data$total_rate))
ggplot() + geom_point(aes(analysis_data$PM_25, linear_model_total$residuals)) +
  geom_smooth(aes(analysis_data$PM_25, linear_model_total$residuals), 
              method = "lm")



#compare models - cross validate, f tests, out of sample prediction

```

Visualizing coefficients - Figure 2
```{r}
#png("Figure2_1.png")
plot_summs(linear_model_total,
           simple_linear_total,
           no_year_total_rate,
           linear_model_SCST,
           simple_linear_SCST,
           no_year_SCST_rate,
           omit.coefs = "log_vis",
           robust = TRUE,
           model.names = c("Total: Original", 
                           "Total: No NL",
                           "Total: Only District FE",
                           "SC/ST: Original", 
                           "SC/ST: No NL",
                           "SC/ST: Only District FE")) + 
  xlab("PM 2.5 Coefficient Estimate") + ggtitle("Enrollment Rate per capita")
#dev.off()



#png("Figure2_2.png")
plot_summs(linear_total_per,
           simple_linear_total_per,
           no_year_total_per,
           linear_SCST_per,
           simple_linear_SCST_per,
           no_year_SCST_per,
           omit.coefs = "log_vis",
           robust = TRUE,
           model.names = c("Total: Original",
                           "Total: No NL",
                           "Total: Only district FE",
                           "SC/ST: Original",
                           "SC/ST: No NL",
                           "SC/ST: Only district FE")) + 
  xlab("PM 2.5 Coefficient Estimate") + ggtitle("Enrollment Rate per 100,000")
#dev.off()


grouped = analysis_data %>% 
  group_by(STATNAME) %>% 
  summarise(b0 = coef(lm(total_rate ~ PM_25 + DISTNAME + log_vis + Year))[1],
            b1 = coef(lm(total_rate ~ PM_25 + DISTNAME + log_vis + Year))[2])


#Plotting PM 2.5 and Enrollment to show surprising results - likely confound
```

Bootstrap confidence intervals 
```{r}

# function to obtain regression weights
bs <- function(formula, data, indices) {
  d <- data[indices,] # allows boot to select sample
  fit <- felm(formula, data=d)
  return(coef(fit))
}

boot_error <- function(data, specification){
# bootstrapping with R replications, put PM beta first
results <- boot(data=data, statistic=bs,
   R=1000, formula= specification$formula)
return(c(quantile(results$t[,1], .025), quantile(results$t[,1], .975)))
}
```

Figure 2 take 2
```{r}
model_bounds = c(boot_error(analysis_data, linear_model_total),
                                  boot_error(gdp_pm_educ, gdp_total_rate),
                                  boot_error(gdp_pm_educ, limited_NL),
                                  boot_error(gdp_pm_educ, both_NL_GDP),
                                  boot_error(analysis_data, simple_linear_total))

PM_coefs_rate = tibble("Model" = c("Night Lights (n = 3027)",
                              "GDP (n = 665)",
                              "Night Lights (n = 665)",
                              "GDP and Night Lights (n = 665)",
                              "No Controls  (n = 3027)"),
                  "lower" = model_bounds[c(1,3,5,7,9)],
                  "upper" = model_bounds[c(2,4,6,8,10)],
                  "coefficient" = c(summary(linear_model_total)$coefficients[1],
                                        summary(gdp_total_rate)$coefficients[1],
                                        summary(limited_NL)$coefficients[1],
                                        summary(both_NL_GDP)$coefficients[1],
                                        summary(simple_linear_total)$coefficients[1]))

pdf("figure2_unscaled.pdf", height = 4, width = 7)
ggplot(PM_coefs_rate, aes(x = Model, y = coefficient, color = Model)) +
  geom_point(size = 2) +
  theme_classic() +
  geom_errorbar(aes(ymin = lower, ymax =  upper)) + 
  geom_hline(yintercept = 0, size = 1, linetype="dashed")+ 
  ylab("%\u0394 enrollment rate per 5 point \u0394 PM 2.5") + 
  xlab("Model specification") +
  theme(axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        axis.text.y = element_text(face = "bold",
                                   size = 14),
        axis.title = element_text(face = "bold",
                                   size = 14), 
        legend.title = element_text(face="bold",
                                      size = 14),
        plot.margin=unit(c(1,1,1,1.5),"cm")) +
  scale_color_wsj()

dev.off()
```


CHECKING FOR NON LINEARITY - Non-significant quadratic term for both
```{r}

#Quadratic model, SC/ST total 
quad_model = felm(SCST_total_rate ~ poly(PM_25, 2, raw = T) + log_vis | Year + DISTNAME,
             data= analysis_data)
summary(quad_model)

#Check if error is normally distributed
ggplot() + geom_histogram(aes(quad_model$residuals))
#Check if predictions have patterns / heteroskedasticity
ggplot() + geom_point(aes(quad_model$fitted.values, analysis_data$SCST_total_rate))
ggplot() + geom_point(aes(analysis_data$PM_25, quad_model$residuals)) +
  geom_smooth(aes(analysis_data$PM_25, quad_model$residuals), 
              method = "lm")

#Quadratic model, total rate 
quad_model = felm(total_rate ~ poly(PM_25, 2, raw = T) + log_vis | Year + DISTNAME,
             data= analysis_data)
summary(quad_model)


ggplot() + geom_histogram(aes(quad_model$residuals))
#Check if predictions have patterns / heteroskedasticity
ggplot() + geom_point(aes(quad_model$fitted.values, analysis_data$total_rate))
ggplot() + geom_point(aes(analysis_data$PM_25, quad_model$residuals)) +
  geom_smooth(aes(analysis_data$PM_25, quad_model$residuals), 
              method = "lm")
```

Visualization
```{r}
pred_sc_st_p = educ_PM$PM_25*prelim_model$coefficients[1] + educ_PM$PM_25^2*prelim_model$coefficients[2]

plot(y = pred_sc_st_p, x= educ_PM$PM_25, type="p",las=1,ylab="SC/ST Primary Enrollment",xlab="PM 2.5 (micrograms per cubic meter)")

hist(educ_PM$PM_25, las=1,ylab="SC/ST Primary Enrollment",xlab="PM 2.5 (micrograms per cubic meter)")

educ_PM %>% 
  group_by(STATNAME) %>% 
  ggplot(aes(x = STATNAME, y = PM_25)) + 
  geom_boxplot() +
  facet_wrap(~STATNAME, scale="free")
```


India PM2.5
```{r}

range = seq(0,125,by = 5)

png("india_districts_pm16.png")  
plot(india_districts_sf["pm16"], breaks = range, axes = FALSE)
title(main = "Average PM 2.5 micrograms per cubic meter in India (2016)",
      cex.main = 1,
      font.main= 4)
dev.off()

png("india_districts_pm15.png")  
plot(india_districts_sf["pm15"], breaks = range, axes = FALSE)
title(main = "Average PM 2.5 micrograms per cubic meter in India (2015)",
      cex.main = 1,
      font.main= 4)
dev.off()

png("india_districts_pm14.png")  
plot(india_districts_sf["pm14"], breaks = range, axes = FALSE)
title(main = "Average PM 2.5 micrograms per cubic meter in India (2014)",
      cex.main = 1,
      font.main= 4)
dev.off()

png("india_districts_pm13.png")  
plot(india_districts_sf["pm13"], breaks = range, axes = FALSE)
title(main = "Average PM 2.5 micrograms per cubic meter in India (2013)",
      cex.main = 1,
      font.main= 4)
dev.off()

png("india_districts_pm12.png")  
plot(india_districts_sf["pm12"], breaks = range, axes = FALSE)
title(main = "Average PM 2.5 micrograms per cubic meter in India (2012)",
      cex.main = 1,
      font.main= 4)
dev.off()

png("india_districts_pm11.png")  
plot(india_districts_sf["pm11"], breaks = range, axes = FALSE)
title(main = "Average PM 2.5 micrograms per cubic meter in India (2011)",
      cex.main = 1,
      font.main= 4)
dev.off()
```

Mapping enrollment
```{r}
median_PM_dist = analysis_data %>% group_by(DISTNAME) %>% summarise(median_PM = median(PM_25))
bad_PM_dist = analysis_data %>% group_by(DISTNAME) %>% summarise(bad_PM = sd(PM_25) + median(PM_25))

base_model = lm(total_rate ~ PM_25 + log_vis + total_count + Year + DISTNAME, data=analysis_data)


median_PM_df = inner_join(median_PM_dist, analysis_data, by = "DISTNAME") %>% mutate(PM_25 = median_PM)
bad_PM_df = inner_join(bad_PM_dist, analysis_data, by = "DISTNAME") %>% mutate(PM_25 = bad_PM)

bad_PM_df <- bad_PM_df %>% 
  mutate(enroll_bad = predict.lm(base_model, newdata = bad_PM_df),
         enroll_median = predict.lm(base_model, newdata = median_PM_df),
         diff = enroll_median - enroll_bad) %>%
  select(DISTNAME, diff) %>% unique()


enroll_map = inner_join(mutate(india_districts_sf, DISTNAME = toupper(NAME_2)),
           bad_PM_df,
           by = "DISTNAME") %>% 
  inner_join(select(analysis_data, TOT_P, DISTNAME), by = "DISTNAME") %>%
  mutate(students_affected = diff*TOT_P)

sum(enroll_map$students_affected, na.rm = T)

ggplot(enroll_map) + geom_histogram(aes(students_affected))

effects_map = ggplot() +
  geom_sf(data = enroll_map, aes(fill = students_affected), color = "NA") + 
  theme_void() +
  theme(axis.text = element_blank(),
        axis.ticks = element_blank(),
        legend.title = element_text(face = "bold", 
                                    size = 14),
        legend.position = "right",
        legend.box = "vertical",
        plot.margin=unit(c(1,0,0,0),"cm")) +
  scale_fill_gradient(name= "Decrease in \nEnrollment Rate \n(1000 students)", 
                        na.value = "grey50",
                      limits = c(0,25000), 
                      breaks=c(0,5000,10000,15000,20000,25000))

```


Figure 3: Heterogeneity of effects
1. Avg PM 2.5
2. Avg. NL and avg GDP
3. SC/ST vs. Total

```{r}
fig3_NL_data = analysis_data %>% 
  group_by(DISTNAME) %>%
  summarise(mean_PM_25 = mean(PM_25),
            mean_log_vis = mean(log_vis))

quantile(fig3_NL_data$mean_log_vis)
quantile(fig3_NL_data$mean_PM_25)

fig3_NL_data = inner_join(fig3_NL_data, analysis_data, by = "DISTNAME")

fig3_NL_data <- fig3_NL_data %>%
  mutate(cat_mean_log_vis = case_when(
    mean_log_vis < 0.5787712 ~ "I",
    mean_log_vis > 0.5787712 & mean_log_vis < 0.8658024 ~ "II",
    mean_log_vis > 0.8658024 & mean_log_vis < 1.2351013 ~ "III",
    TRUE ~ "IV"),
    cat_mean_PM = case_when(
    mean_PM_25 < 25.45 ~ "I",
    mean_PM_25 > 25.45 & mean_PM_25 < 34.86667 ~ "II",
    mean_PM_25 > 34.86667 & mean_PM_25 < 52.56667 ~ "III",
    TRUE ~ "IV"))


fig3_model = felm(total_rate ~ PM_25 + log_vis + total_count + PM_25:cat_mean_PM|Year + DISTNAME,
                  data = fig3_NL_data)


coef = 500*c(c(0,fig3_model$coefficients[4:6]) + fig3_model$coefficients[1])

# bootstrapping with R replications, put PM beta first
results <- boot(data=fig3_NL_data, statistic=bs,
   R=1000, formula= fig3_model)
e1= sd(results$t[,1])
e2 = sqrt(sd(results$t[,4])^2 + e1^2 + 2*cov(results$t[,1], results$t[,4]))
e3 = sqrt(sd(results$t[,5])^2 + e1^2 + 2*cov(results$t[,1], results$t[,5]))
e4 = sqrt(sd(results$t[,6])^2 + e1^2 + 2*cov(results$t[,1], results$t[,6]))

error = 500*c(e1, e2, e3, e4)
name2 = c("I", "II", "III", "IV")

p1 = ggplot(data = data.frame(coef, error, name), 
            aes(y = coef, x = name)) + 
  geom_point() +  
  theme_apa() +
  geom_errorbar(aes(ymin = coef - 1.96*error, ymax =  coef + 1.96*error)) + 
  geom_hline(yintercept = 0, size = 1, linetype="dashed")+ 
  ylab("% change in enrollment rate") + 
  theme(axis.text = element_text(face = "bold",
                                 size = 14),
        axis.title = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        plot.margin=unit(c(1,1,0,1),"cm"))

PM_hist = ggplot(fig3_NL_data) + 
  geom_density(aes(mean_PM_25), fill = "darkgrey", alpha = 0.4) +  
  theme_apa() +
  xlab("Mean PM 2.5 Level (Quartiles) (μg/m^3)") +
  ylab("Density") + 
  theme(axis.text.x = element_text(face = "bold",
                                 size = 14),
        axis.text.y = element_text(size = 12),
        axis.title = element_text(face = "bold",
                                  size = 14), 
        axis.title.y = element_blank(),
        axis.ticks = element_blank(),
        plot.margin=unit(c(0.25,1,0.4,1),"cm"))

p1 = plot_grid(p1, PM_hist, nrow = 2, rel_heights=c(4, 3))



fig3_model2 = felm(total_rate ~ PM_25 + log_vis + total_count + PM_25:cat_mean_log_vis|Year + DISTNAME,
                  data = fig3_NL_data)


coef2 = 500*c(c(0,fig3_model2$coefficients[4:6]) + fig3_model2$coefficients[1])
# bootstrapping with R replications, put PM beta first
results <- boot(data=fig3_NL_data, statistic=bs,
   R=1000, formula= fig3_model2)
e1= sd(results$t[,1])
e2 = sqrt(sd(results$t[,4])^2 + e1^2 + 2*cov(results$t[,1], results$t[,4]))
e3 = sqrt(sd(results$t[,5])^2 + e1^2 + 2*cov(results$t[,1], results$t[,5]))
e4 = sqrt(sd(results$t[,6])^2 + e1^2 + 2*cov(results$t[,1], results$t[,6]))

error2 = 500*c(e1, e2, e3, e4)
name2 = c("I", "II", "III", "IV")

p2 = ggplot(data = data.frame(coef2, error2, name2), 
            aes(y = coef2, x = name2)) + 
  geom_point() +  
  theme_apa() +
  geom_errorbar(aes(ymin = coef2 - 1.96*error2, ymax =  coef2 + 1.96*error2)) + 
  geom_hline(yintercept = 0, size = 1, linetype="dashed")+ 
  ylab("%Δenrollment rate per 5 point ΔPM 2.5") + 
  xlab("Mean Log Night Light Intensity (Quartiles)") +
  theme(axis.text = element_text(face = "bold",
                                 size = 14),
        axis.title = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        plot.margin=unit(c(0.4,1,0,1),"cm"))

vis_hist = ggplot(fig3_NL_data) + 
  geom_density(aes(mean_log_vis), fill = "darkgrey", alpha = 0.4) +  
  theme_apa() +
  xlab("Mean Log Night Light Intensity (Quartiles)") +
  ylab("Density") + 
  theme(axis.text.x = element_text(face = "bold",
                                   size = 14),
        axis.text.y = element_text(size = 12),
        axis.title = element_text(face = "bold",
                                  size = 14), 
        axis.title.y = element_blank(),
        axis.ticks = element_blank(),
        plot.margin=unit(c(0.25,1,1,1),"cm"))

p2 = plot_grid(p2, vis_hist, nrow = 2, rel_heights =c(4, 3))

error3 = c(boot_error(analysis_data, total_rate ~ PM_25 + log_vis + total_count | Year + DISTNAME),
           boot_error(analysis_data, SCST_total_rate ~ PM_25 + log_vis + total_count | Year + DISTNAME))

PM_coefs_rate = tibble("Model" = c("Total: With Night Lights",
                              "SC/ST: With Night Lights"),
                  "error_min" = 500*c(error3[1],error3[3]),
                  "error_max" = 500*c(error3[2],error3[4]),
                  "coefficient" =500*c(summary(linear_model_total)$coefficients[1],
                                        summary(linear_model_SCST)$coefficients[1]))

p3 = ggplot(PM_coefs_rate, aes(x = Model, y = coefficient, color = Model)) +
  geom_point(size = 2) +
  theme_apa() +
  geom_errorbar(aes(ymin = error_min, ymax =  error_max)) + 
  geom_hline(yintercept = 0, size = 1, linetype="dashed")+ 
  ylab("%Δenrollment rate per 5 point ΔPM 2.5") + 
  xlab("Model Population") +
  theme(axis.text = element_text(face = "bold",
                                   size = 14),
        axis.title = element_text(face = "bold",
                                   size = 14), 
        axis.title.y = element_blank(),
        legend.position = "none",
        plot.margin=unit(c(1,1,1,1),"cm")) +
  scale_x_discrete(labels=c("Total: With Night Lights" = "Total", 
                            "SC/ST: With Night Lights" = "SC/ST")) +
  scale_color_wsj()


rhs= plot_grid(p1, p2,labels = c("c","d"), nrow = 2, rel_widths = c(1,1.5), label_size = 16)
lhs= plot_grid(effects_map, p3,labels = c("a","b"), nrow = 2, rel_heights  = c(1.5,1), label_size = 16)

pdf("figure3_v3.pdf", height = 8, width = 10)
plot_grid(lhs, rhs, ncol = 2,labels = "a", rel_widths = c(1.25,1), label_size = 16)
dev.off()
```



```{r}
total_effect = analysis_data %>% mutate(total_pop = (total_primary + total_upper)/total_rate,
                         SCST_pop = (sc_st_primary+sc_st_upper)/SCST_total_rate) %>% 
  select(DISTNAME,
         total_pop,
         SCST_pop)
total_effect = total_effect %>% mutate(total_affected = total_pop*linear_model_total$coefficients[1])


```



Just PM, just NL, transformed variables effect on heteroskedasticity - for appendix
check for which dmsp data
send email
drop negative NL and then see if estimate if remains the same
check for different with no negative and negative
email marshall for district GDP

Proving the heterogeneity point:
```{r}
toy_df = tibble(y = c(10, 5, 8, 4),
                x = c(5, 2.5, 6, 3),
                sex = c("M", "M", "F", "F"))
coef(lm(y~x, data = toy_df))[2]
mean(coef(lm(y~x, data = filter(toy_df, sex == "F")))[2],
     coef(lm(y~x, data = filter(toy_df, sex == "M")))[2])

```

